---
title: "Final Project"
author: "AwesomePie1453"
date: '2023-11-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## It's the Final Project

# duh nuh nuh, duh duh duh duh duh, duh duh duh, duh duh duh duh duh duhuhh

I hope you enjoy my rendition of the Final Countdown up above. Go Europe, am I right?

Alright, so this project will be me expanding my horizons in R Markdown using statistics, which I previously haven't done in R. I am attempting to make a project through R and knit it through github so you can just access it via the link. There will be multiple files here to access.


### Parlays

This project is designed to look at those who bet parlays in a larger sample and see what sets them apart. This is the exploratory analyses for my larger paper to be written this winter. I was not able to finish all the analyses due to time, but it gives me a good starting point, so I appreciate it! 

## Read in the data

This is from our longitudinal study, wave 4, where the majority of these analyses will be conducted.

```{r load in the data}
library(haven)
library(dplyr)
library(tidyverse)
library(Hmisc)
Data <- read_sav("BGSU0007_merged_w5_OUTPUT copy.sav")
Wave_4 <- as_tibble(Data) %>%
  select(caseid_w5, starts_with("W5_"))
```

Now, let's look at our main variable, whether or not people endorsed betting parlays

```{r frequencies}
table(Wave_4$"W5_Q146_2")
```
Okay, so in this case, 1 = endorsed, 2 = did not endorse. That is the case for the majority of my binary variables. 

Now, in this dataset I have a bunch of new variables looking at parlays specifically. I want to know what their frequencies are as well. 

```{r new parlay question}
Wave_4 %>%
  summarise(ParlayYes=sum(W5_Q146_2 ==1, na.rm=TRUE),
           ParlayNo=sum(W5_Q146_2 ==2, na.rm=TRUE),
           N = ParlayYes + ParlayNo,
           Parlay_Percent = ParlayYes / N,
           WinMoney = sum(W5_Q189_1 ==1, na.rm=TRUE),
           WinMoneyNo=sum(W5_Q189_1 ==2, na.rm=TRUE),
           WinMoney_Percent = WinMoney / ParlayYes,
          Fun = sum(W5_Q189_2 ==1, na.rm=TRUE),
           FunNo=sum(W5_Q189_2 ==2, na.rm=TRUE),
           Fun_Percent = Fun / ParlayYes,
          Action = sum(W5_Q189_3 ==1, na.rm=TRUE),
           ActionNo=sum(W5_Q189_3 ==2, na.rm=TRUE),
           Action_Percent = Action / ParlayYes,
          Payout = sum(W5_Q189_4 ==1, na.rm=TRUE),
           PayoutNo=sum(W5_Q189_4 ==2, na.rm=TRUE),
           Payout_Percent = Payout / ParlayYes,
          Boosted = sum(W5_Q189_5 ==1, na.rm=TRUE),
           BoostedNo=sum(W5_Q189_5 ==2, na.rm=TRUE),
           Boosted_Percent = Boosted / ParlayYes,
          Other = sum(W5_Q189_6 ==1, na.rm=TRUE),
           OtherNo=sum(W5_Q189_6 ==2, na.rm=TRUE),
           Other_Percent = Other / ParlayYes,
          Neg200 = sum(W5_Q190 ==1, na.rm=TRUE),
          Neg200_Percent = Neg200 / ParlayYes,
          Even_200 = sum(W5_Q190 ==2, na.rm=TRUE),
          Even_200_Percent = Even_200 / ParlayYes,
          F100_200 = sum(W5_Q190 ==3, na.rm=TRUE),
          F100_200_Percent = F100_200 / ParlayYes,
          F200_500 = sum(W5_Q190 ==4, na.rm=TRUE),
          F200_500_Percent = F200_500 / ParlayYes,
          F500_1000 = sum(W5_Q190 ==5, na.rm=TRUE),
          F500_1000_Percent = F500_1000 / ParlayYes,
          F1K_2K = sum(W5_Q190 ==6, na.rm=TRUE),
          F1K_2K_Percent = F1K_2K / ParlayYes,
          F2K_5K = sum(W5_Q190 ==7, na.rm=TRUE),
          F2K_5K_Percent = F2K_5K / ParlayYes,
          F5K_10K = sum(W5_Q190 ==8, na.rm=TRUE),
          F5K_10K_Percent = F5K_10K / ParlayYes,
          F10K = sum(W5_Q190 ==9, na.rm=TRUE),
          F10K_Percent = F10K / ParlayYes,
          FOther = sum(W5_Q190 ==10, na.rm=TRUE),
          FOther_Percent = FOther / ParlayYes,
          LoseLot = sum(W5_Q191 ==1, na.rm=TRUE),
          LoseLot_Percent = LoseLot / ParlayYes,
          LoseLittle = sum(W5_Q191 ==2, na.rm=TRUE),
          LoseLittle_Percent = LoseLittle / ParlayYes,
          BreakEven = sum(W5_Q191 ==3, na.rm=TRUE),
          BreakEven_Percent = BreakEven / ParlayYes,
          WinSome = sum(W5_Q191 ==4, na.rm=TRUE),
          WinSome_Percent = WinSome / ParlayYes,
          WinLot = sum(W5_Q191 ==5, na.rm=TRUE),
          WinLot_Percent = WinLot / ParlayYes
          )
```

Enjoy the massive table above. Let me write down some of the key parts here.

206 people (51.89%) of the sample endorsed betting parlays. Why did they bet parlays? 83% did it to win money, 71.8% because it was fun, 38.8% to have action on multiple games, 47.6% for the potential of a high payout, 33% due to boosted odds tokens.

As far as the odds they are typically betting, its fairly normal. I made these number brackets up arbitrarily for what I thought made sense. Let's look at a frequency distrubtion of it

```{r typical bet}
frequency_table<- dplyr::count(Wave_4, W5_Q190)
```



```{r typical outcome}
dplyr::count(Wave_4, W5_Q191)
```
The typical parlay outcome is pretty normal, asshown below.


Okay now that we know our variables, its time to do some T tests. Go to ttest.rmd to see it.


