---
title: "Other analyses"
author: "AwesomePie1453"
date: '2023-12-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load in the data}
library(haven)
library(dplyr)
library(tidyverse)
library(Hmisc)
library(ggplot2)
Data <- read_sav("BGSU0007_merged_w5_OUTPUT copy.sav")
Wave_4 <- as_tibble(Data) %>%
  select(caseid_w5, starts_with("W5_"))
```
## R Markdown

I would like to do way more than the ones below. But, I don't have a ton of time. So let me hit the most important ones.

I talked about timing before, this is big. Inplay vs live.

```{r}
model <- aov(W5_Q146_2 ~ W5_Q145, data = Wave_4)
summary(model)
```
Lets try Tukeys. I'm sure I can figure it out. 
* narrator voice*
He did not figure it out in time. 

```{r sports}
model <- lm(W5_Q146_2  ~ W5_Q75_1 + W5_Q75_2 + W5_Q75_3 + W5_Q75_4 + W5_Q75_5 + W5_Q75_6 + W5_Q75_7 + W5_Q75_8 + W5_Q75_9 + W5_Q75_10 + W5_Q75_11, data = Wave_4)
summary(model)
```
Oh interesting. So 1, 2, 4, 9 which are basektball, baseball, football and motor sports. Motor sports??


Now lets do type of bets

```{r type}
model <- lm(W5_Q146_2  ~ W5_Q146_1 + W5_Q146_3 + W5_Q146_4 + W5_Q146_5 + W5_Q146_6 + W5_Q146_7, data = Wave_4)
summary(model)
```
Here we got totals, player props, and prop bets. More unique. 

Now let's do substances 

```{r substances}
model <- lm(W5_Q146_2  ~ W5_Q165_1 + W5_Q165_2 + W5_Q165_3 + W5_Q165_4 + W5_Q165_5 + W5_Q165_6 + W5_Q165_7 + W5_Q165_8 + W5_Q165_9, data = Wave_4)
summary(model)
```

Marijuana is the only significant with parlay, again. That's so weird. 

Knowledge! Knowledge! 


```{r knowledge}
model <- lm(W5_Q146_2  ~ W5_Q134_a + W5_Q134_b + W5_Q134_c + W5_Q134_d + W5_Q134_e + W5_Q134_f + W5_Q134_g + W5_Q134_h + W5_Q134_i + W5_Q134_j + W5_Q134_k, data = Wave_4)
summary(model)
```
I think i broke it. Ohhhh well. 


```{r illicit behaviors}
model <- lm(W5_Q146_2  ~ W5_Q185_1 + W5_Q185_2 + W5_Q185_3 + W5_Q185_4 + W5_Q185_5 + W5_Q185_6 + W5_Q185_7 + W5_Q185_8 + W5_Q185_9 + W5_Q185_10 + W5_Q185_11 + W5_Q185_12 + W5_Q185_13 + W5_Q185_14, data = Wave_4)
summary(model)
```
Nothing, not too shocking 

W5_Q52_1

```{r wherebet}
model <- lm(W5_Q146_2  ~ W5_Q52_1 + W5_Q52_2 + W5_Q52_3 + W5_Q52_4 + W5_Q52_5, data = Wave_4)
summary(model)
```
Just 1 and 4, which are smartphone and... against friends?? 

W5_Q126_multi_1

```{r events}
model <- lm(W5_Q146_2  ~ W5_Q126_multi_1 + W5_Q126_multi_2 + W5_Q126_multi_3 + W5_Q126_multi_4 + W5_Q126_multi_5 + W5_Q126_multi_6 + W5_Q126_multi_7 + W5_Q126_multi_8, data = Wave_4)
summary(model)
```
3 and 8, MLB playoffs and College football playoffs. 


# future directions 

regression with substances
regression with knowledge 
satisfaction of life 
Motives 
stuff (pgsi, positive play'0 ) predicting the other pgsi questions, whether they win esp, but also typical odds, and reasons why. 

clean it up 