---
title: "Ttest"
author: "AwesomePie1453"
date: '2023-12-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## T Tests

Here is the first of my ttests. Very basic, do those who bet parlays differ on whether they live in a legal  gambling state or no.

```{r LegalState}
t_test <- t.test(W5_Q73 ~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
It appears that those who bet parlays were more likely to have legal gambling. Makes sense.

```{r freqadv}
t_test <- t.test(W5_Q70 ~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

No difference in frequency of avertisements. That's dissapointing.

```{r online}
t_test <- t.test(W5_Q40_p~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
No difference, interesting. Online gamlbers NOT more likely to bet parlays.(check these numbers)

```{r sportsfreq}
t_test <- t.test(W5_GambFreq_c~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
these p valuesare weird, that seems significant to me. Parlay gamblers have higher frequency of betting sports - makes sense (1 to 6)


```{r timing}
t_test <- t.test(W5_Q145~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
again with p-value of 1, well this is timing. It makes sense, i might need to recode this one thoguh (or anova?)


Type of sports bets (not with parlays). They should be connected to other bets, but lets see. Those who bet parlays, are they more likely to bet... moneylines?

```{r moneylines}
t_test <- t.test(W5_Q146_1~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Nope. Spreads?
```{r spreads}
t_test <- t.test(W5_Q146_3~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Oh yeah. Totals?

```{r totals}
t_test <- t.test(W5_Q146_4~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```


Yessir. Player props?

```{r player props}
t_test <- t.test(W5_Q146_5~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

For sure. Player props?

```{r player prop}
t_test <- t.test(W5_Q146_6~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
yup, not shocking now. Fianlly, futures?

```{r Futures}
t_test <- t.test(W5_Q146_7~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Even futures. Everything but moneylines. That's super interesting

###Sports

Now we are gonna look at sports! Start with basketball

```{r basketball}
t_test <- t.test(W5_Q75_1~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

yup, feel like these will all be connected. might need a regression for these sports? Not running them all yet


Do people who bet parlays more liely to drink while betting?

```{r alcohol}
t_test <- t.test(W5_Q165_1~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
close but not quite

```{r freqalcohol}
t_test <- t.test(W5_Q159_a~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r marijuana}
t_test <- t.test(W5_Q165_3~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

marijuana was with parlays.. weird

```{r alcohol}
t_test <- t.test(W5_Q165_5~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
but not cocaine


```{r none}
t_test <- t.test(W5_Q165_11~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

no difference in none

```{r percalc}
t_test <- t.test(W5_Q161_grid_a~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

nothing here

Okay KNOWLEDGE here we go

```{r knowlbasket}
t_test <- t.test(W5_Q134_a~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
close hmmm

```{r knowlbase}
t_test <- t.test(W5_Q134_b~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowlsoccer}
t_test <- t.test(W5_Q134_c~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowlfoot}
t_test <- t.test(W5_Q134_d~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowlhockey}
t_test <- t.test(W5_Q134_e~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowltennis}
t_test <- t.test(W5_Q134_h~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

Tennis, interesting. But wait. Its lower??? Woah. I wont look at other sports yet

let look at march amdness
W5_Q126_multi_2

```{r kmarch madness}
t_test <- t.test(W5_Q126_multi_2~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Woah! Msarch madness bettors like parlays.

```{r Cross state lines}
t_test <- t.test(W5_Q82~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
```{r seekingtereatment}
t_test <- t.test(W5_Q92~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r how many drinks}
t_test <- t.test(W5_Q180~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r concern gambling}
t_test <- t.test(W5_Q111_g~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```