---
title: "Ttest"
author: "AwesomePie1453"
date: '2023-12-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load in the data}
library(haven)
library(dplyr)
library(tidyverse)
library(Hmisc)
library(ggplot2)
Data <- read_sav("BGSU0007_merged_w5_OUTPUT copy.sav")
Wave_4 <- as_tibble(Data) %>%
  select(caseid_w5, starts_with("W5_"))
```
## T Tests

Welcome to my ttest section. I am going to run some basic ttests with my parlay variable to see what those bettors might vary on.

# Basic

Okay, do those bet parlays see more betting advertisements?

```{r freqadv}
t_test <- t.test(W5_Q70 ~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

No difference in frequency of advertisements. 

Let's look at frequency of sports betting.

```{r sportsfreq}
t_test <- t.test(W5_GambFreq_c~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Parlay bettors bet sports more. Good to know. (The 1 p-value threw me off but I guess it is just so small?)


```{r timing}
t_test <- t.test(W5_Q145~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Again with p-value of 1, well this is timing. It makes sense, I might need to make this one an ANOVA.

# Type of Sports Bets

Other type of sports bets (not with parlays). They should be connected to other bets, but lets see. Those who bet parlays, are they more likely to bet... moneylines?

```{r moneylines}
t_test <- t.test(W5_Q146_1~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Nope. Spreads?

```{r spreads}
t_test <- t.test(W5_Q146_3~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Oh yeah. Totals?

```{r totals}
t_test <- t.test(W5_Q146_4~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```


Yessir. Player props?

```{r player props}
t_test <- t.test(W5_Q146_5~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

For sure. Player props?

```{r player prop}
t_test <- t.test(W5_Q146_6~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
yup, not shocking now. Fianlly, futures?

```{r Futures}
t_test <- t.test(W5_Q146_7~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Even futures. Everything but moneylines. That's super interesting.

### Sports

Now we are gonna look at sports! Start with basketball

```{r basketball}
t_test <- t.test(W5_Q75_1~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

yup, feel like these will all be connected. might need a regression for these sports? Not running them all yet.

### Substances

Do people who bet parlays more likely to drink while betting?

```{r alcohol}
t_test <- t.test(W5_Q165_1~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Close but not quite. Marijuana?

```{r marijuana}
t_test <- t.test(W5_Q165_3~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

Marijuana was with parlays.. weird

```{r cocaine}
t_test <- t.test(W5_Q165_5~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
But not cocaine.

### Knowledge

A large part of my research looks at the percieved knowledge that someone has in gambling on certain sports. Typically, I think breaking it by sport is more useful. However, for this one I do want to look at a potential mean variable.

```{r mutate}
Wave_4$KnowledgeMean <- rowMeans(Wave_4[, c("W5_Q134_a", "W5_Q134_b", "W5_Q134_c", "W5_Q134_d", "W5_Q134_e", "W5_Q134_f", "W5_Q134_g", "W5_Q134_h", "W5_Q134_i", "W5_Q134_j", "W5_Q134_k")], na.rm = TRUE)
```

Oops, it hates my NAs. I'll figure that out later. I'm gonna choose the biggest American sports. Basketball, Baseball, Soccer, Football, Hockey. 
```{r knowlbasket}
t_test <- t.test(W5_Q134_a~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
```{r knowlbase}
t_test <- t.test(W5_Q134_b~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowlsoccer}
t_test <- t.test(W5_Q134_c~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowlfoot}
t_test <- t.test(W5_Q134_d~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

```{r knowlhockey}
t_test <- t.test(W5_Q134_e~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Okay, none of them. I wonder if there is a correlation with tennis knowledgde, since that's a weird one.

```{r knowltennis}
t_test <- t.test(W5_Q134_h~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```

Hmmmmm. Lower knowledge for those betting parlays. That's actually crazy. ts lower??? Woah. I wont look at other sports yet.

### Other

For curiosity, what about those who bet March Madness? Feels like a parlay event. 

```{r kmarch madness}
t_test <- t.test(W5_Q126_multi_2~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Woah! March madness bettors like parlays.

#Treatment

Are parlay bettors more likely to seek treatment?

```{r seekingtereatment}
t_test <- t.test(W5_Q92~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
No. Are they more concerned about their gambling?

```{r concern gambling}
t_test <- t.test(W5_Q111_g~ W5_Q146_2, var.equal=FALSE, paired = FALSE, alternative="less", Wave_4)

t_test
```
Not enough.

Okay, this is enough for the T-tests. Let's wrap it up with some other analyses. I'll see you in OtherAnalysis.rmd
